%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Core Member} % Affiliation/role
{Vision and Language Group, IIT Roorkee} % Organisation/group
{Roorkee, India} % Location
{May, 2021 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item Core member of VLG, a student group that promotes \textbf{Deep Learning research culture} at IITR by discussing relevant research papers, organizing workshops and working on related projects.
    \item Involved in paper discussions, contributing to projects, organizing workshops,etc.
  \end{cvitems}
}

%---------------------------------------------------------

\cventry
{Core Member, Open Source and Development} % Affiliation/role
{Data Science Group, IIT Roorkee} % Organisation/group
{Roorkee, India} % Location
{February, 2022 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item Part of a 30-member strong team which aims to foster the culture of Machine Learning and Deep Learning at IIT Roorkee.
		\item Organized weekly paper discussions and workshops for the benefit of the IITR student community.
	\end{cvitems}
}

%----------------------------------------


\cventry
{Core Member} % Affiliation/role
{Programming and Algorithms Group, IIT Roorkee} % Organisation/group
{Roorkee, India} % Location
{October, 2021 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item {Core member of PAG, a student run community that fosters the culture of \textbf{Competetive Programming in IITR}}
		\item {Involved in conducting contests, organizing open lectures etc.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Core Member} % Affiliation/role
{InfoSec, IIT Roorkee} % Organisation/group
{Roorkee, India} % Location
{March, 2021 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item {Member of a group of information security enthusiasts who believe in freedom of information and privacy while maintaining ethical and legal acpects. Took part in a lot of \textbf{CTFs} around the world}
		\item {Involved in organizing CTFs, conducting open discussions, organizing workshops etc.}
	\end{cvitems}
}



 \cventry
{Junior Member} % Affiliation/role
{Finance Club, IIT Roorkee} % Organisation/group
{Roorkee, India} % Location
{March, 2021 - January, 2022} % Date(s)
{
	\begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item {Actively involved in cultivating a robust \textbf{financial culture in IITR} by organizing workshops, competitions and writing blogs.}
		\item {Enthusiastically participated in various projects and group discussions on the latest research and developments}
	\end{cvitems}
}
%---------------------------------------------------------

\end{cventries}
